Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-03-01 paper/snakemajoranas.tex
make 'small gap' explicit

\comment{The gap is small because of long trajectories.}
One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap; which is the non-zero density of states near zero energy.
One of the mechanisms giving rise to a soft gap is the reduction of the induced gap for states with the momentum directed along the junction.
From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor, shown in Fig.~\ref{fig:setup}(a).
These long trajectories have long flight times $\tau_\textrm{f} \approx L_\textrm{t} / v_F$ (see Fig.~\ref{fig:setup}), where $L_\textrm{t}$ is the trajectory length.
Equivalently, the Thouless energy of these trajectories $E_{\textrm{Th}}=\hbar / \tau_\textrm{f}$ is small, resulting in a small gap.
This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, making a low filling of the bands a possible workaround\cite{nijholt2015orbital}.
However, low filling requires precise knowledge of the system and is more sensitive to disorder or microscopic inhomogeneities.
On the other hand, disorder scatters these long trajectories and introduces a cutoff on the scale of the mean free path~\cite{haim_double-edge_2018}; however, disorder is impossible to control to a required precision experimentally.

\begin{figure}[!htb]
\centering
\includegraphics[width=0.9\columnwidth]{figures/zigzag.pdf}
\caption{The straight (top) and the zigzag (bottom) SNS junction.
The zigzag pattern has a peak-to-peak amplitude $z_y$ and a period $z_x$.
The yellow areas are superconductors with a phase difference of $\phi$ between the top and the bottom.
The middle area is the semiconductor of width $W$.
A magnetic field $B$ pointing in the $x$-direction causes a Zeeman splitting in the semiconductor
A trajectory traveling at a grazing angle (red curve) has a very long flight time $\tau_\textrm{f}$ and a very small induced gap $E_\textrm{gap}$.
At the same time, the zigzag geometry limits the length of a trajectory therefore lowering $\tau_\textrm{f}$ and increasing $E_\textrm{gap}$.
\label{fig:setup}}
\end{figure}

>>>>

\comment{The gap is small because of long trajectories.}
One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap; which is the non-zero density of states near zero energy.
One of the mechanisms giving rise to a soft gap is the reduction of the induced gap for states with the momentum directed along the junction.
From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor, shown in Fig.~\ref{fig:setup}(a).
These long trajectories have long flight times $\tau_\textrm{f} \approx L_\textrm{t} / v_F$ (see Fig.~\ref{fig:setup}), where $L_\textrm{t}$ is the trajectory length.
Equivalently, the Thouless energy of these trajectories $E_{\textrm{Th}}=\hbar / \tau_\textrm{f}$ is small, resulting in a small gap $E_\textrm{gap} \ll \Delta$.
This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, making a low filling of the bands a possible workaround\cite{nijholt2015orbital}.
However, low filling requires precise knowledge of the system and is more sensitive to disorder or microscopic inhomogeneities.
On the other hand, disorder scatters these long trajectories and introduces a cutoff on the scale of the mean free path~\cite{haim_double-edge_2018}; however, disorder is impossible to control to a required precision experimentally.

\begin{figure}[!htb]
\centering
\includegraphics[width=0.9\columnwidth]{figures/zigzag.pdf}
\caption{The straight (top) and the zigzag (bottom) SNS junction.
The zigzag pattern has a peak-to-peak amplitude $z_y$ and a period $z_x$.
The yellow areas are superconductors with a phase difference of $\phi$ between the top and the bottom.
The middle area is the semiconductor of width $W$.
A magnetic field $B$ pointing in the $x$-direction causes a Zeeman splitting in the semiconductor
A trajectory traveling at a grazing angle (red curve) has a very long flight time $\tau_\textrm{f}$ and a very small induced gap $E_\textrm{gap} \ll \Delta$.
At the same time, the zigzag geometry limits the length of a trajectory therefore lowering $\tau_\textrm{f}$ and increasing $E_\textrm{gap}$.
\label{fig:setup}}
\end{figure}
